Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex
Correct title/idea for this workshop

\title{Personal Social Machines}

@@

% Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
\def\plaintitle{Personal Social Machines}
\def\plainauthor{Daniel A. Smith, Max Van Kleek, Nigel R. Shadbolt}
\def\plainkeywords{social machines, personal data, linked data}
\def\plaingeneralterms{Social Machines, Personal Data}

@@

>>>>

\title{Using Distributed Information Stores for Patient-Clinician Health Data Sharing}

@@

% Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
\def\plaintitle{Using Distributed Information Stores for Patient-Clinician Health Data Sharing}
\def\plainauthor{Daniel A. Smith, Max Van Kleek, Nigel R. Shadbolt}
\def\plainkeywords{personal data, patient care, healthcare, information stores}
\def\plaingeneralterms{Personal Data, Patient Care, Healthcare, Information Stores}

@@

Electronic integrated health records have...
